\documentclass[12pt]{article}

% House style preamble: central symlink only.
\input{.house-style/preamble.tex}

% Anonymization toggle for double-blind review.
\newif\ifblind
\ifdefined\blindbuild \blindtrue \else \blindfalse \fi

\hypersetup{
  pdftitle={Was magnitude estimation necessary? A secondary-data reassessment of Bard, Robertson, and Sorace (1996)},
  pdfkeywords={magnitude estimation, acceptability judgments, grammaticality judgments, secondary data, experimental syntax}
}
\ifblind\hypersetup{pdfauthor={}}\fi

\title{Was magnitude estimation necessary?\\
{\large A secondary-data reassessment of Bard, Robertson, and Sorace (1996)}}
\ifblind
  \author{[Author name, ORCID, and affiliation removed for double-blind review]}
\else
  \author{Brett Reynolds \orcidlink{0000-0003-0073-7195}%
  \thanks{Contact: \href{mailto:brett.reynolds@humber.ca}{brett.reynolds@humber.ca}}\\
  Humber Polytechnic \& University of Toronto}
\fi
\date{June 2026}

\begin{document}
\maketitle

\begin{abstract}
This paper reassesses Bard, Robertson, and Sorace's case for magnitude
estimation in linguistic acceptability research. It separates two claims that
are often run together: acceptability judgments are graded, measurable, and
methodologically serious; magnitude estimation has a practical advantage over
simpler formal judgment tasks. The first claim is the stronger legacy. The
second requires later method-comparison evidence.

The paper reports a constrained secondary analysis of public Sprouse
method-comparison data, within an approved reuse boundary and guided by an
analysis charter fixed before outcome analysis. The reanalysis finds strong
cross-method convergence and bounded response-function curvature, but no
systematic practical resolution advantage for magnitude estimation in these
data. Langsford et al.\ enter as article-level evidence about reliability and
response-style risks, while computational benchmarks remain afterlife evidence
rather than evidence about magnitude estimation itself.
\end{abstract}

\noindent\textbf{Keywords:} magnitude estimation; acceptability judgments; grammaticality judgments; secondary data; experimental syntax

\input{sections/01-problem}
\input{sections/02-bard-target}
\input{sections/03-secondary-data-design}
\input{sections/04-scale-and-reliability}
\input{sections/05-contemporary-afterlife}
\input{sections/06-grammaticality-and-acceptability}
\input{sections/07-conclusion}

\section*{Data and code availability}

No raw participant-level data is committed to this repository. Source and
dataset verification are tracked in \texttt{notes/source-verification.md}; the
analysis charter and structural Sprouse inventory are tracked in
\texttt{notes/analysis-charter.md} and \texttt{notes/dataset-inventory.md}.
Jon Sprouse approved reuse for the limited secondary methodological analysis
described in the charter after checking with Diogo Almeida.

The manuscript reports summary diagnostics rather than redistributing
participant-level rows or derived participant-level tables. Scripts generate
ignored local structural derivatives, readiness manifests, and descriptive
item/contrast signal, dimensionality, response-function, and pair-level
robustness outputs under \texttt{data/derived/}; participant-level raw files
remain outside the repository.

The local reproduction recipe is documented in \texttt{analysis/README.md}. The
analysis charter was versioned in Git and fixed before outcome analysis as an
internal analysis record rather than an external registry entry.

\section*{Acknowledgements}

AI-assisted tools were used in the development of this paper. OpenAI Codex
(GPT-5) was used for project planning, source-tracking support, analysis-script
drafting, and prose revision. Claude Opus was used for simulated reviewer
feedback during an advisory-board pass. The author directed the research
questions, obtained the data-use permission, verified sources, interpreted the
analysis outputs, and takes responsibility for the final text.

\clearpage
\printbibliography

\end{document}
