\section{The problem}

Bard, Robertson, and Sorace made a methodological claim that was larger than a
single elicitation format. Acceptability judgments, they argued, could be
treated as graded measurements rather than as informal binary verdicts
\parencite{BardEtAl1996}. That move helped make experimental syntax a
measurement enterprise: judgments could be collected from naive participants,
scaled, compared across groups, and subjected to ordinary statistical tests.

The harder question is whether magnitude estimation was necessary for that
advance. Magnitude estimation promised a way around the scale restrictions of
traditional judgment tasks, giving participants an open response scale and
preserving fine distinctions. But later acceptability work did not settle into
one privileged elicitation method. Likert ratings, forced choice, yes/no tasks,
and Thurstonian models all became part of the measurement toolkit
\parencite{sprouse2013,LangsfordEtAl2018,sprouse2017}.

This paper separates two claims that are often allowed to travel together. One
claim is strong and still plausible: acceptability is graded, measurable, and
methodologically serious. The other is weaker: magnitude estimation has a
practical measurement advantage over simpler formal tasks. The first claim can
survive even if the second does not.

The empirical half of this is not untouched. The methodology literature has
already compared elicitation formats and largely deflated magnitude
estimation's special status. \textcite{schutze2016} reports that most or all of
its advertised advantages over Likert tasks have since been refuted, pointing to
\textcite{weskott2011} and \textcite{sprouse2013}; later work weighed the formats
on convergence \parencite{sprouse2013}, statistical power \parencite{sprouse2017},
and reliability and response style \parencite{LangsfordEtAl2018}.

So the bare verdict that magnitude estimation carries no special advantage is
not what this paper adds. The contribution is to separate that verdict from the
durable measurement claim, to relocate acceptability within a projectibility
account, and to route each later dataset to a prespecified estimand, so that any
reanalysis of public comparison data, once reuse is permitted, cannot quietly
select whichever scale looks best.

The reassessment is therefore not a rejection of Bard et al.'s programme. It is
a test of what should be credited to magnitude estimation itself, and what
should instead be credited to the broader formalization of acceptability
judgment methodology.
