\section{Secondary-data design}

The secondary-data design treats the project as a measurement reassessment of
Bard, Robertson, and Sorace \parencite{BardEtAl1996}. Four kinds of source
should stay separate (distinct from the evidential channels of
Section~\ref{sec:gramm-accept}; these are sources routed to estimands, not
channels into a profile). Published summaries from Bard et al.\ can source the
historical claim, but not a direct replication unless their participant-level
data is found.

Later judgment studies can support secondary analysis when they compare
elicitation methods on shared or comparable items and provide the rows needed
for the intended estimand. Computational benchmarks can show the afterlife of
acceptability labels, but they do not bear on magnitude estimation versus
Likert ratings. Construct-level discussion can separate acceptability from
grammaticality, naturalness, standardness, and correction.

\begin{table}[t]
\centering
\small
\begin{tabular}{@{}>{\raggedright\arraybackslash}p{0.19\linewidth}>{\raggedright\arraybackslash}p{0.22\linewidth}>{\raggedright\arraybackslash}p{0.25\linewidth}>{\raggedright\arraybackslash}p{0.24\linewidth}@{}}
\toprule
Source & Evidence level & Use in this paper & Claim it cannot support \\
\midrule
Bard et al.\ 1996 & Published article & Historical target and scale-resolution claim & Direct replication without participant rows \\
Sprouse 2013/2017 & Public row-level comparison data & Constrained secondary method comparison within approved reuse boundary & Raw-data redistribution or drift beyond the approved methodological scope \\
Langsford et al.\ 2018 & Published article and supplement & Reliability and response-style synthesis & New participant-level reliability model without raw rows \\
CoLA, BLiMP, SAD & Benchmark labels and documentation & Afterlife of formal acceptability measurement & Evidence about ME versus other human judgment methods \\
\bottomrule
\end{tabular}
\caption{Evidential routing before analysis. ME = magnitude estimation; SAD =
Syntactic Acceptability Dataset.}
\label{tab:evidence-routing}
\end{table}

The approved reuse boundary resolves the Sprouse side of the genre gate. Public
row-level data from the Sprouse comparison studies can now support a constrained
secondary analysis of method performance.
The Langsford et al.\ reliability study is essential evidence for the argument,
but unless its raw participant responses are obtained it can only constrain the
paper at the article-summary level. The paper should therefore not promise a
full response-style or test-retest model across the whole literature.

The Sprouse files also require representation choices before modelling. For
\textcite{sprouse2013}, the primary forced-choice comparison should use the
pair-level sign-test file, because forced choice is a pairwise task and that
file already records judgments against expected patterns. The logistic file
preserves item-level binary rows, changing the unit of analysis, so it belongs
as a named sensitivity specification.

For \textcite{sprouse2017}, yes/no rows with item IDs \texttt{B},
\texttt{G}, and \texttt{M} should be excluded from item-level comparisons.
They are absent from the materials workbook, occur in repeated early order
positions for every subject, and do not align with the magnitude-estimation,
Likert, or forced-choice item universe. This exclusion is a structural
inclusion rule, not an outcome-based trimming decision.

Before any modelling, each source should be assigned to an estimand it can
actually answer. The primary estimand is the item-level acceptability signal
recoverable across methods. Secondary estimands are method-specific noise or
bias and decision agreement for theoretically relevant contrasts.

Participant response style and method-by-item instability are admissible only
when the dataset contains the participant-level rows and repeated structure
needed to estimate them. This ordering keeps the analysis from selecting
whichever scale looks best after the fact, the kind of forking path Gelman and
Loken warn about \parencite{GelmanLoken2013,gelman2014statcrisis}.

The substantive comparison is a measurement null, but a careful one. Magnitude
estimation, Likert ratings, forced choice, and Thurstonian choice are modelled
as readings of a common item-level acceptability signal through method-specific
response functions, not as the same signal plus method noise: the bounded
methods can compress the signal at the extremes, while the open ratio scale need
not. The single-dimension assumption should be checked before any
method-specific term is read, by comparing a one-factor model against
correlated-two-factor and bifactor alternatives and checking method residuals
for item-level structure where the data support that comparison.

This ordering matters because the advantage Bard et al.\ actually claimed is
about resolution, recovering distinctions that fixed scales censor
\parencite[35]{BardEtAl1996}. A plain common-signal-plus-noise null would book
that resolution as magnitude-estimation noise and let the method only lose; the
response functions and the dimensionality check let a resolution advantage
register instead. If one factor suffices, magnitude estimation still has to earn
its term; if it does not, the analysis turns to where the methods diverge.
Scrambled labels, method-label permutations, and simulations from the
response-function model remain negative controls for the pipeline, not the
substantive comparison.
