\section{Scale and reliability}

The scale question should be phrased as practical measurement advantage over
the response-function measurement null set out in the secondary-data design.
Bard et al.'s case for magnitude estimation included scale resolution,
fine-grained distinctions, naive-participant use, and replication across groups
\parencite[32]{BardEtAl1996}. The safer target is that source-grounded claim,
together with the stronger reading of magnitude estimation that took hold in
parts of the later methodology literature.

Later method-comparison data give the paper a sharper question: does magnitude
estimation recover item differences, participant agreement, or theoretically
relevant decisions that simpler tasks lose, and in particular does it recover
graded distinctions that bounded scales compress at the extremes?

\textcite{sprouse2013} compare formal judgment tasks with informal published
judgments, giving evidence about convergence between magnitude estimation,
Likert ratings, and forced choice. The public Sprouse rows can support a
bounded reanalysis of item-level agreement and decision consequences within
the approved reuse boundary. \textcite{LangsfordEtAl2018} add a reliability and
response-bias target by comparing Likert, magnitude estimation, forced choice,
and Thurstonian models. Without their raw rows, Langsford can support the
synthesis of published reliability findings but not a new participant-level
response-style or test-retest model.

The reliability analysis inherits the unit-of-analysis charter fixed in the
secondary-data design rather than reopening it. The same primary and sensitivity
representations carry over, so reliability claims stay traceable to fixed units
of analysis instead of to whichever representation later proves most convenient.

The primary comparison weighs methods on resolution, prediction, decision
consequences, and convergence, prioritising consequences for the linguistic
contrast. Resolution is the criterion Bard's claim lives on: whether magnitude
estimation recovers graded item differences that bounded scales compress at
ceiling or floor, or a measurement dimension that survives the dimensionality
check. Reliability is a distinct property, not a proxy for it;
\textcite{LangsfordEtAl2018} report magnitude estimation as less reliable, which
does not by itself settle resolution.

For this paper, a practical magnitude-estimation advantage would have to change
an inferential decision. A summary-statistic improvement alone would not count.
It would count if magnitude estimation recovered a good-vs-bad contrast that
bounded methods missed, showed its largest extra spread exactly where bounded
scales compressed the response, carried a stable method-specific dimension
across scoring choices, or reduced sign-error or exaggeration risk for a named
contrast under a design analysis. A larger correlation, by itself, would not
settle the question.

The Sprouse reanalysis gives a narrow answer. Magnitude estimation and the
bounded methods share a strong item-level signal. Raw Likert means also show the
expected bounded response-function curvature relative to magnitude estimation.
That curvature is the pattern Bard's scale argument makes visible, but the
endpoint and pair-level diagnostics do not show a systematic practical
distinction preserved only by magnitude estimation.

The dimensionality result is deliberately modest. It is a first-pass aggregate
check of the item and contrast matrices, used to ask whether a clear
multidimensional rescue for magnitude estimation appears in the available
Sprouse summaries. It does not replace a full participant-level factor model,
which would require a broader row-level evidence base than this paper has.

\begin{table}[t]
\centering
\small
\begin{tabular}{@{}>{\raggedright\arraybackslash}p{0.23\linewidth}>{\raggedright\arraybackslash}p{0.34\linewidth}>{\raggedright\arraybackslash}p{0.34\linewidth}@{}}
\toprule
Diagnostic & Sprouse et al.\ 2013 & Sprouse and Almeida 2017 \\
\midrule
ME--Likert convergence & Condition \(r=.986\); pair \(r=.963\) & Item \(r=.925\); pair \(r=.944\) \\
First-pass dimensionality check & Aggregate pair matrix: first component 89.4\%; second eigenvalue below parallel-analysis threshold & Aggregate item and pair matrices: first components 80.6\% and 85.9\%; second eigenvalues below thresholds \\
Bounded response function & Bounded logistic improves over linear; endpoint ME SDs .142 and .175 versus middle .313 & Bounded logistic improves over linear; endpoint ME SDs .249 and .321 versus middle .349 \\
Pair robustness & Bounded predictors \(R^2=.926\); no ME top-quartile pair falls in the bounded bottom half & Bounded predictors \(R^2=.901\); no ME top-quartile pair falls in the bounded bottom half \\
\bottomrule
\end{tabular}
\caption{Sprouse diagnostics for Bard's resolution claim. ME = magnitude
estimation. The dimensionality row is an aggregate first-pass check, and the
response-function rows use magnitude estimation as an unbounded diagnostic axis
rather than the true latent acceptability scale.}
\label{tab:sprouse-diagnostics}
\end{table}

Table~\ref{tab:sprouse-diagnostics} therefore separates three facts. First, the
aggregate matrices provide no obvious multidimensional rescue for magnitude
estimation. Second, the Likert scale behaves like a bounded response function,
so a fair null should allow compression. Third, the available Sprouse contrasts
do not show the further pattern that would make magnitude estimation
practically superior: endpoint regions are not where magnitude estimation
spreads out most, and good-vs-bad pairs ranked highly by magnitude estimation
are also ranked highly by bounded methods.

These aggregate practical diagnostics are weaker than posterior certainty
statements or formal equivalence tests. They show that the available contrasts
lack the predicted ME-only pattern; they leave open participant-level method
factors, response-style dimensions, and locally dependent item effects.

Type S and Type M errors enter only as properties of estimating a named contrast
at a given sample size, not as properties a format carries. The relevant
question is whether choosing magnitude estimation rather than another method
changes the sign-error probability or the exaggeration ratio for a specific
contrast under a design analysis \parencite{gelman2014types}. Sensitivity checks
should vary transformations and exclusion rules as named specifications rather
than as invisible post hoc choices \parencite{steegen2016increasing}.
