\section{The contemporary afterlife of acceptability}

Contemporary benchmark resources show what survived from the formal
acceptability programme, but it is worth being exact about what survived. CoLA
turns examples from linguistics publications into binary labels for model
evaluation \parencite{WarstadtEtAl2019CoLA}; BLiMP turns expert-designed
grammatical contrasts into large sets of minimal pairs
\parencite{WarstadtEtAl2020}. What they inherit is the portability of contrasts,
the idea that acceptability-related distinctions can be made portable, scored,
and compared across systems. What they inherit it through is the expert-asterisk
channel, not Bard et al.'s naive-participant graded measurement.

They also change the evidential object. CoLA's labels come from published
linguistic examples rather than from a new sample of naive participant
responses. BLiMP's contrasts are generated from expert-crafted grammars and
then used to test whether a model prefers the acceptable sentence in a pair.
Those are useful evaluation resources, but they are not method-comparison data
for magnitude estimation, Likert ratings, forced choice, or yes/no judgments.

The Syntactic Acceptability Dataset is the most useful bridge case because it
keeps grammatical status and crowd acceptability status apart
\parencite{juzek2024}. That separation is exactly the level discipline this
paper needs. So the split is clean: the portability of contrasts survived into
CoLA and BLiMP through the expert channel, while Bard's graded naive-participant
measurement migrated only into crowdsourced resources like the Syntactic
Acceptability Dataset. Benchmark labels show the afterlife of one channel;
participant-response datasets are still needed to compare human elicitation
methods.
