\section{Grammaticality and acceptability}\label{sec:gramm-accept}

The reassessment also needs a disciplined vocabulary. The background view
adopted here is that grammar is a system of projectibility profiles
\parencite{Goodman1955}: relatively stable patterns that license inferences from
forms, meanings, contexts, speakers, and judgments to uses a community or
register treats as available. Profiles are projectible for a purpose: here,
predicting how a construction behaves across speakers, registers, and tasks well
enough to support theoretical and applied syntactic claims. A grammaticality
claim is therefore not a report of one response. It states what a form projects
to: interpretation, production, correction, expert classification, register fit,
cross-speaker stability, and related consequences.

Three of these are observation channels, not the target. Participant responses
under an acceptability prompt are observations of judgments under a task. Expert
asterisks and published example labels are classifications made within a
theoretical or editorial practice. Benchmark labels are dataset-construction
decisions. The profile itself is the fourth thing: the structure of inferences a
form licenses, what its acceptability, production, correction, expert
classification, register fit, and cross-speaker stability jointly project to. Two
channels are evidence about the same profile when they bear on the same form's
projection relations.

So the profile is not the average of the channels, and channel disagreement is
not noise to smooth away. When a sentence is rated low by naive participants,
left unstarred in the literature, and attested in a register corpus, the verdict
about its profile is fixed by which inferences actually hold, tested against
further data, not by a vote across channels. A channel that consistently fails to
predict the others is then evidence about that channel, not about the profile.
This is what makes the profile more than an unweighted set of labels, and it is
the identity condition the level discipline needs.

This discipline keeps neighbouring constructs apart. Acceptability is one
evidential route into a projectibility profile, not the profile itself. Personal
production, naturalness, standardness, correction behaviour, and theoretical
classification project differently. A sentence can be dispreferred without
being ungrammatical, correctable without being unnatural, or standard in one
register while unacceptable under another task framing.

This is where the framing earns its place in the measurement argument, not just
in the vocabulary. If acceptability is one route into a multidimensional profile,
a single acceptability scalar should be insufficient exactly where the channels
come apart: items participants rate low but the literature leaves unstarred, or
that are standard in one register and degraded under another task framing. Those
are the items where the dimensionality gate in the secondary-data design should
break, and where magnitude estimation's open scale, if it carries a second
dimension, should diverge from the bounded tasks. The projectibility account
therefore makes a testable prediction about the method comparison, not only a
distinction.

Bard et al.\ helped make one part of this space measurable: graded
acceptability judgments from participants \parencite{BardEtAl1996}. That is a
major contribution to the measurement of one evidential channel. It does not by
itself show that an acceptability scale captures every inference licensed by a
grammar. Later benchmarks sometimes repackage acceptability-related labels as
grammaticality targets \parencite{WarstadtEtAl2019CoLA,WarstadtEtAl2020}. The
Syntactic Acceptability Dataset is valuable here because it explicitly
separates literature-derived grammatical status from crowd acceptability status
\parencite{juzek2024}.

That boundary also limits the no-new-data paper. Existing datasets can compare
the stability of elicitation methods and clarify how acceptability labels
travel. They cannot settle a full projectibility profile for a construction:
production, correction, register, interpretation, and community licensing would
require data designed for those inferences.
