\section{Conclusion}

The balanced update is straightforward. Bard et al.\ were right to make
acceptability measurable and methodologically serious. Their documented case
for magnitude estimation concerned scale resolution, fine distinctions,
naive-participant use, and replication across groups
\parencite[32]{BardEtAl1996}. That claim deserves credit as part of the
history of experimental syntax.

The method-specific conclusion is more limited, and it has to be tested fairly.
Magnitude estimation is compared against a measurement null in which later
formal tasks read a common item-level acceptability signal through
method-specific response functions, and in which the single-dimension assumption
is itself tested before any method-specific term is read. The question is then
whether magnitude estimation earns its keep on resolution, the distinctions Bard
argued fixed scales censor, or on prediction, decision stability, or construct
interpretation, rather than whether it survives a null that books resolution as
noise.

This paper approximates that design with the available Sprouse evidence:
aggregate cross-method item and contrast matrices, response-function
diagnostics, and pair-level robustness checks. That scope matters because a
full participant-level dimensionality model across Bard, Sprouse, and Langsford
would require rows that have not been found.

The Sprouse reanalysis supports that narrower update. Magnitude estimation,
Likert ratings, forced choice, and yes/no judgments share a strong practical
signal in the available comparison data. First-pass aggregate dimensionality
checks show no obvious evidence against a single dominant dimension at that
level of aggregation. Raw Likert means show bounded response-function
curvature, which is exactly why the null should not treat bounded tasks as
simple noisy copies of magnitude estimation.

The remaining resolution diagnostics are less favourable to the stronger method
claim: endpoint regions do not show unusually large magnitude-estimation
spread, and pair-level bounded predictors recover most magnitude-estimation
contrast variance. Langsford et al.\ still enter at the article level unless
their raw responses become available.

The projectibility payoff is correspondingly modest. Formal judgments project
stable item-level contrast ordering across ordinary elicitation formats in the
available Sprouse data, while magnitude estimation alone does not project an
additional practical ordering for the tested contrasts.

The conclusion would change under a clear ME-only pattern: endpoint regions
with much larger ME spread than middle regions, high-ME contrasts that bounded
methods consistently placed low, stable method-specific residual structure
across scoring choices, or lower sign-error and exaggeration risk for named
linguistic contrasts. Those are the patterns the present Sprouse diagnostics do
not show.

The central conclusion is therefore stable. The durable legacy is the formal
measurement of graded acceptability as one route into grammar's projectibility
profiles. The broader privileged status sometimes read into magnitude
estimation is a separate claim, and later evidence has to earn it separately.
